%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Classicthesis-Styled CV
% LaTeX Template
% Version 1.0 (22/2/13)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Alessandro Plasmati
%
% License:
% CC BY-NC-SA 3.0 (http://creativecommons.org/licenses/by-nc-sa/3.0/)
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass{scrartcl}

\reversemarginpar % Move the margin to the left of the page 

\newcommand{\MarginText}[1]{\marginpar{\raggedleft\itshape\small#1}} % New command defining the margin text style

\usepackage[nochapters]{classicthesis} % Use the classicthesis style for the style of the document
\usepackage[LabelsAligned]{currvita} % Use the currvita style for the layout of the document

\renewcommand{\cvheadingfont}{\LARGE\color{Maroon}} % Font color of your name at the top

\usepackage{hyperref} % Required for adding links	and customizing them
\hypersetup{colorlinks, breaklinks, urlcolor=Maroon, linkcolor=Maroon} % Set link colors

\newlength{\datebox}\settowidth{\datebox}{Aug 2015} % Set the width of the date box in each block

\newcommand{\NewEntry}[3]{\noindent\hangindent=2em\hangafter=0 \parbox{\datebox}{\small \textit{#1}}\hspace{1em} #2 #3 % Define a command for each new block - change spacing and font sizes here: #1 is the left margin, #2 is the italic date field and #3 is the position/employer/location field
\vspace{0.5em}} % Add some white space after each new entry

\newcommand{\NewEntrySmall}[3]{\noindent\hangindent=2em\hangafter=0 \parbox{\datebox}{\small \textit{#1}}\hspace{-1em} #2 #3 % Define a command for each new block - change spacing and font sizes here: #1 is the left margin, #2 is the italic date field and #3 is the position/employer/location field
\vspace{0.5em}} % Add some white space after each new entry


\newcommand{\Description}[1]{\hangindent=2em\hangafter=0\noindent\raggedright\footnotesize{#1}\par\normalsize\vspace{1em}} % Define a command for descriptions of each entry - change spacing and font sizes here

\usepackage[vmargin=0.75in, left=1.75in, right=1.5in]{geometry}

%----------------------------------------------------------------------------------------

\begin{document}

\thispagestyle{empty} % Stop the page count at the bottom of the first page

%----------------------------------------------------------------------------------------
%	NAME AND CONTACT INFORMATION SECTION
%----------------------------------------------------------------------------------------

\begin{cv}{\spacedallcaps{Katie Shamash}}\vspace{1.5em} % Your name

\noindent\spacedlowsmallcaps{Contact details}\vspace{0.5em} % Personal information heading

\NewEntry{address}{18 Sussex St., Flat 5, London, UK, SW1V 4RW} % Address

\NewEntry{email}{\href{mailto:k.shamash@protonmail.com}{k.shamash@protonmail.com}} % Email address

\NewEntry{twitter}{\href{http://www.twitter.com/katieshamash}{@katieshamash}} % Twitter

\NewEntry{phone}{+44 7548 253935} % Phone number(s)

\vspace{1em} % Extra white space between the personal information section and goal

%----------------------------------------------------------------------------------------
%	WORK EXPERIENCE
%----------------------------------------------------------------------------------------

\noindent\spacedlowsmallcaps{Work Experience}\vspace{1em}

\NewEntry{Aug 2015-Present}{Scholarly communications analyst, \textsc{Jisc}}

\Description{\MarginText{Jisc (London)}Worked directly with relevant stakeholders to improve data quality and transparency. Gathered data from a wide range of sources and analyzed it in a systematic and reproducible way. Clearly communicated findings to non-technical audiences through blog posts, interactive visualizations, reports, and presentations. Successfully influenced publisher negotiations and funder policies with data-driven evidence. Tested and refined dashboard software with end users to deliver a marketable product.}

%------------------------------------------------

\NewEntry{May-Aug 2015}{Research assistant, \textsc{Simon Fraser University}}

\Description{\MarginText{Simon Fraser University (Vancouver)}Prepared an extensive literature review surveying the humanities monograph industry. Conducted research into university presses' digital initiatives. Connected university presses with complementary strengths and interests to spur innovation.}

%------------------------------------------------

\NewEntry{2011-2012}{Freelance editor, \textsc{Second Generation Press}}

\Description{\MarginText{Second Generation Press (Montreal)}Edited works prior to publication, reviewed manuscripts, and advised digital production strategy.}

%------------------------------------------------

\NewEntry{2011}{Web sales \& marketing manager, \textsc{Black Rose Books}}

\Description{\MarginText{Black Rose Books (Montreal)}Doubled social media following, wrote newsletters and press releases, managed interns.}

%------------------------------------------------

\vspace{1em} % Extra space between major sections

%----------------------------------------------------------------------------------------
%	EDUCATION
%----------------------------------------------------------------------------------------

\spacedlowsmallcaps{Education}\vspace{1em}

\NewEntry{2014-2015}{Master of Publishing candidate}

\Description{\MarginText{Simon Fraser University (Vancouver)}Multidisciplinary program with classes on technology, history, design, marketing, and industry of trade, magazine, and academic publishing. Hands-on projects include a course project on data analysis for scholarly communication, which used topic modelling, natural language processing, and network visualization to visualize and interpret scholarly journal data.
}


%------------------------------------------------

\NewEntry{2009-2014}{Bachelor of Arts \& minor in Computer Science}
	
\Description{\MarginText{Concordia University (Montreal)}Graduated with distinction\ \ $\cdotp$\ \ \textit{Honours English and Creative Writing}\ \ $\cdotp$\ \ \textit{Minor in Computer Science}\newline
Relevant computer science courses include probability and statistics, combinatorics,
object-oriented programming, data structures and algorithms,
mathematics for computer science, and
functional and logical programming.}

%------------------------------------------------
\NewEntry{2008-2009}{Dipl\^{o}me d'\'{e}tudes coll\'{e}giales}

\Description{\MarginText{Marianopolis College (Montreal)}Dean's list student\ \ $\cdotp$\ \ \textit{Creative arts, literature, and languages}\newline
}

%------------------------------------------------


\vspace{1em} % Extra space between major sections

%----------------------------------------------------------------------------------------
%	PUBLICATIONS
%----------------------------------------------------------------------------------------

\spacedlowsmallcaps{Publications and presentations}\vspace{1em}

\NewEntrySmall{2018}{Navigating the complex terrain of open access}

\Description{\MarginText{Special issue}A special journal issue showcasing achievements of institutions in promoting open access. Currently in submission stage. \textit{Sage Open}.
 \\Guest editors: Frank \textsc{Manista}, ~Mafalda \textsc{Marques}, ~Katie \textsc{Shamash}, ~Graham \textsc{Stone}
}

\NewEntrySmall{2017}{Reassembling scholarly communications: an evaluation of the Andrew W. Mellon Foundation’s monograph initiative}

\Description{\MarginText{Journal article}A consideration of the Andrew W. Mellon Foundation’s 2014--2015 scholarly communications initiative, which focused on helping to develop new capacity in the monograph-publishing ecosystem. \textit{The Journal of Electronic Publishing}. \href{http://dx.doi.org/10.3998/3336451.0020.101}{doi:10.3998/3336451.0020.101} \\ Authors: John W. \textsc{Maxwell}, ~Alessandra \textsc{Bordini}, ~Katie \textsc{Shamash}}

%------------------------------------------------

\NewEntrySmall{2016}{Article processing charges and subscriptions: monitoring open access costs}

\Description{\MarginText{Report}The largest-scale analysis of open access charges in the UK. Widely shared on social media, covered in a press article, and made into a podcast. The underlying data and analysis have been used in further research worldwide. An early draft informed the 2015 Tickell report on open access to the Department of Business, Energy, and Industrial Strategy. Prepared for Jisc. \href{https://www.jisc.ac.uk/reports/apcs-and-subscriptions}{jisc.ac.uk/reports/apcs-and-subscriptions} \\Author: Katie \textsc{Shamash}}


%------------------------------------------------


\NewEntrySmall{2015}{Teaching data analysis in the social sciences: a case study with article level metrics}

\Description{\MarginText{Book chapter}A book chapter on how open scholarly communications data can be used to build data literacy and skills for humanities students. \textit{Open Data as Open Educational Resources}. Eds. Atenas, J. and Havemann, L. \href{http://dx.doi.org/10.6084/m9.figshare.1590031}{doi:10.6084/m9.figshare.1590031}
 \\ Authors: Katie \textsc{Shamash}, ~Juan Pablo \textsc{Alperin}, ~Alessandra \textsc{Bordini}
}


\Description{\MarginText{Presentations}2017\ \ $\cdotp$\ \ "Article processing charges and subscriptions: Monitoring open access costs in the United Kingdom" \ \ $\cdotp$\ \  \textsc{OpenAIRE} \ \ $\cdotp$\ \  Oslo}





\Description{2016\ \ $\cdotp$\ \ "Seven key findings on article processing charges" \ \ $\cdotp$\ \  \textsc{Open Access Good Practice} \ \ $\cdotp$\ \  Bath}



\Description{2016\ \ $\cdotp$\ \ "Making sense of open scholarly communications data" \ \ $\cdotp$\ \  \textsc{Digifest} \ \ $\cdotp$\ \  Birmingham}


\vspace{1em} % Extra space between major sections
%----------------------------------------------------------------------------------------
%	SKILLS
%----------------------------------------------------------------------------------------

\spacedlowsmallcaps{Skills}\vspace{1em}

\Description{\MarginText{Languages}English (native speaker), French (fluent)}

\Description{\MarginText{Data analysis}Python, R, SQL, Excel, OpenRefine, Weka}

\Description{\MarginText{Mathematics}Probability and statistics, machine learning, natural language processing, network analysis}

\Description{\MarginText{Design}HTML, CSS, Adobe InDesign, \LaTeX}

\Description{\MarginText{Visualisation}Tableau, Javascript (D3.js), Matplotlib, Gephi}

\Description{\MarginText{Office}Windows, Linux, Microsoft Office}

%------------------------------------------------

%----------------------------------------------------------------------------------------

\end{cv}

\end{document}